\sysfull

### 2019-06-24 paper/TOSN/hwswsetup.tex
First iteration

\subsection{Experimental Setup}
\label{sec:results_hardware_software}
\add{
We used three different setups to evaluate \sys: 
(i) an RF-powered energy-harvesting device, WISP\,5.1~\cite{wisp5,wisp}, with a fixed capacitor size of 47\,$\mu$f; 
(ii) an MSP-EXP430FR5969 launchpad~\cite{MSP-EXP430FR5969_launchpad} powered by a BQ25570~\cite{BQ25570EVM-206_website} solar power harvester that is connected to an IXYS SLMD121H04L solar cell~\cite{SLMD121H04L_website} for experimenting with different energy buffers; and
(iii) an MSP-EXP430FR5969 launchpad~\cite{MSP-EXP430FR5969_launchpad} that is continuously powered.
}

@@

WISP contains the MSP430FR5969~\cite{wolverine} MCU with 64\,kB of
non-volatile (FRAM) memory and 2\,kB of volatile (SRAM) memory and was
configured to 1\,MHz clock speed.
%
We powered WISP using an RF signal generator emitting a 20\,dBm sinusoidal wave at 915\,MHz.
The signal generator was connected to the Laird RFMAX S9028PCRJ 8\,dBic
antenna~\cite{atlas2015}.
%
The antenna was oriented towards and in parallel with WISP's antenna, and
no objects obstructed the path.
%
We affixed WISP with a paper harness at the edge of a table at a height, from the table surface, of 10\,cm.
%
For distance-controlled experiments we positioned WISP at $d=\{15, 30,
50\}$\,cm from the exciter antenna.
%
% We chose relatively shorter distances than in a deployment scenario to reduce
% charge time and run experiments faster, after having confirmed ourselves a
% result also reported in prior work~\cite{alpaca} that the amount of energy
% available in one charge cycle---the sum of stored energy and incoming energy
% during execution---is the same at distances beyond 50\,cm where incoming energy
% becomes negligible.
%
To obtain execution time, the software toggled GPIO pins at sections of the code
under profile, and the Saleae~\cite{saleae} logic analyzer measured
intervals between edges in the signal. For continuous power experiments, the 
execution time was measured using the clock features in TI Code Composer Studio IDE version 7.1.
%
\subsection{Software Benchmarks}
\label{sec:software_benchmarks}

\begin{table}%
\caption{Simulation Configuration}
\label{tab:one}
\begin{minipage}{\columnwidth}
\begin{center}
\begin{tabular}{llll}
  \toprule
		App.&Tasks&SLOC&Description\\
		\hline
        \emph{ar} &10 &428 & activity recognition using a KNN\\ % with a deterministic input from a randomly-generated sequence of accelerometer data\\
        \emph{bc} &10 &371 & several bitcount algorithms\\
        % \textbf{bc} &10 &371 & Counts bits in bytes sequences
% using several algorithms and check for correctness\\
        \emph{cuckoo} &14 &426 & Cuckoo Filter with pseudo-random values\\
        \emph{dijkstra} &5 &198 & Dijkstra shortest path algorithm \\
        \emph{fft} &8 &449 & Fast Fourier Transform\\ % on three pre-generated 128 sample vectors\\
		\emph{sort} &4 &167 & selection sort algorithm\\
  \bottomrule
\end{tabular}
\end{center}
\end{minipage}
\caption{Characteristics of benchmarks used for evaluation.}
\label{table:benchmark_table}
\end{table}%

%\begin{table}
%	\centering
%	\footnotesize
%	\begin{tabular}{| r|r|r | p{0.54\columnwidth} |}
%		\hline
%		App.&Tasks&SLOC&Description\\
%		\hline\hline
%        \emph{ar} &10 &428 & activity recognition using a KNN\\ % with a deterministic input from a randomly-generated sequence of accelerometer data\\
%		\hline
%        \emph{bc} &10 &371 & several bitcount algorithms\\
%        % \textbf{bc} &10 &371 & Counts bits in bytes sequences
%% using several algorithms and check for correctness\\
%		\hline
%        \emph{cuckoo} &14 &426 & Cuckoo Filter with pseudo-random values\\
%		\hline
%        \emph{dijkstra} &5 &198 & Dijkstra shortest path algorithm \\
%		\hline
%        \emph{fft} &8 &449 & Fast Fourier Transform\\ % on three pre-generated 128 sample vectors\\
%		\hline
%		\emph{sort} &4 &167 & selection sort algorithm\\
%		\hline
%	\end{tabular}
%\caption{Characteristics of benchmarks used for evaluation.}
%\label{table:benchmark_table}
%\end{table}

@@

We compare \sys against Alpaca~\cite{alpaca}, the state-of-the-art task-based system for intermittent computing. For a fair comparison the task decomposition of the benchmarks are ensured to be the same for both systems.
%
Since Alpaca's compiler pass is implemented only for LLVM, we could not use that implementation to instrument the benchmarks and compile them with GCC. Instead, we \emph{manually} performed the instrumentation done by the compiler pass. The instrumentation consists of identifying WAR dependencies  and adding code and memory allocations to make a private copy of the affected variables.
% For array variables, instrumentation also includes adding code for dynamically tracking the array access. 
%
%Manual instrumentation of Alpaca code is not a general approach, but only served as a practical alternative to porting the compiler pass from LLVM to GCC.
%
%Our experiments show that manually-instrumented Alpaca code compiled with GCC is about 30\%-40\% faster than Alpaca code instrumented automatically by the Alpaca LLVM compiler pass and compiled with LLVM. This performance difference is due to the early experimental state of the MSP430 backend for LLVM~\cite{baghsorkhi_cgo_2018}.
%
By compiling both systems with the same compiler (GCC), we ensure that our comparison in Section~\ref{sec:evaluation} is fair.

>>>>

\subsection{Experimental Setup}
\label{sec:results_hardware_software}
\add{
We used three different setups to evaluate \sys: 
(i) an RF-powered energy-harvesting device, WISP\,5.1~\cite{wisp5,wisp}, with a fixed capacitor size of 47\,$\mu$F; 
(ii) an MSP-EXP430FR5969 launchpad~\cite{MSP-EXP430FR5969_launchpad} powered by a BQ25570~\cite{BQ25570EVM-206_website} solar power harvester that is connected to an IXYS SLMD121H04L solar cell~\cite{SLMD121H04L_website} for experimenting with different energy buffers; and
(iii) an MSP-EXP430FR5969 launchpad~\cite{MSP-EXP430FR5969_launchpad} that is continuously powered.
}

@@

WISP contains the MSP430FR5969~\cite{wolverine} MCU with 64\,kB of
non-volatile (FRAM) memory and 2\,kB of volatile (SRAM) memory and was
configured to 1\,MHz clock speed.
We powered WISP using an RF signal generator emitting a 20\,dBm sinusoidal wave at 915\,MHz.
The signal generator was connected to the Laird RFMAX S9028PCRJ 8\,dBic
antenna~\cite{atlas2015}.
The antenna was oriented towards and in parallel with WISP's antenna, and
no objects obstructed the path.
We affixed WISP with a paper harness at the edge of a table at a height, from the table surface, of 10\,cm.
For distance-controlled experiments we positioned WISP at $d=\{15, 30,
50\}$\,cm from the exciter antenna.
To obtain execution time, the software toggled GPIO pins at sections of the code
under profile, and the Saleae~\cite{saleae} logic analyzer measured
intervals between edges in the signal. For continuous power experiments, the 
execution time was measured using the clock features in TI Code Composer Studio IDE version 7.1.
%
\subsection{Software Benchmarks}
\label{sec:software_benchmarks}

\begin{table}%
\caption{Simulation Configuration}
\label{tab:one}
\begin{minipage}{\columnwidth}
\begin{center}
\begin{tabular}{llll}
  \toprule
		App.&Tasks&SLOC&Description\\
		\hline
        \emph{ar} &10 &428 & activity recognition using a KNN\\ % with a deterministic input from a randomly-generated sequence of accelerometer data\\
        \emph{bc} &10 &371 & several bitcount algorithms\\
        \emph{cuckoo} &14 &426 & Cuckoo Filter with pseudo-random values\\
        \emph{dijkstra} &5 &198 & Dijkstra shortest path algorithm \\
        \emph{fft} &8 &449 & Fast Fourier Transform\\ % on three pre-generated 128 sample vectors\\
		\emph{sort} &4 &167 & selection sort algorithm\\
  \bottomrule
\end{tabular}
\end{center}
\end{minipage}
\caption{Characteristics of benchmarks used for evaluation.}
\label{table:benchmark_table}
\end{table}%

@@

We compare \sys against Alpaca~\cite{alpaca}, the state-of-the-art task-based system for intermittent computing. For a fair comparison, the task decomposition of the benchmarks is ensured to be the same for both systems.
%
Since Alpaca's compiler pass is implemented only for LLVM, we could not use that implementation to instrument the benchmarks and compile them with GCC. Instead, we \emph{manually} performed the instrumentation done by the compiler pass. The instrumentation consists of identifying WAR dependencies  and adding code and memory allocations to make a private copy of the affected variables.
By compiling both systems with the same compiler (GCC), we ensure that our comparison in Section~\ref{sec:evaluation} is fair.

### 2019-06-24 paper/TOSN/implementation.tex
First iteration

\noindent\textit{Task Transitions.} \texttt{NEXT\_TASK} marks the task to be executed at the 
end of the current one task and it can be invoked along
any control path to dynamically determine the next task.

@@

First the scheduler updates the coalescing target using the coalescing
strategy.  Second, the scheduler resumes a commit, if one is in progress. Third,
the scheduler clears the list of dirty shadow pages. The scheduler then 
sets the program counter to the next task to run, which \sys tracks in  
non-volatile memory.  
%
Before executing the task, \sys checks whether there is a partially committed
task to resume, which requires \sys to restore volatile state, including the program
counter.  
%
If there is no in-progress, partially committed task, \sys starts executing and
coalescing tasks.

>>>>

\noindent\textit{Task Transitions.} \texttt{NEXT\_TASK} marks the task to be executed after the current one task and it can be invoked along
any control path to dynamically determine the next task.

@@

First, the scheduler updates the coalescing target using the coalescing
strategy.  Second, the scheduler resumes a commit, if one is in progress. Third,
the scheduler clears the list of dirty shadow pages. The scheduler then 
sets the program counter to the next task to run, which \sys tracks in  
non-volatile memory.  
%
Before executing the task, \sys checks whether there is a partially committed
task to resume, which requires \sys to restore the volatile state, including the program
counter.  
%
If there is no in-progress, partially committed task, \sys starts executing and
coalescing tasks.

### 2019-06-24 paper/TOSN/paging.tex
TOSN coala version
First iteration

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalesced-war.pdf}
	\caption{Task coalescing-induced WAR dependency (in the case of this example, at variable $x$). Such dynamic dependencies cannot be resolved at compile-time and they break memory consistency.}
	\label{figure:coalescedWar}
\end{figure}

@@

VMM overview is given in Fig.~\ref{figure:mem-man}.
VMM abstracts the physical address space of the non-volatile memory (FRAM) and divides it into \texttt{\underline{private}} and \texttt{\underline{shadow}} (underlined locations are non-volatile) buffers, and each buffer is divided into pages.
\texttt{\underline{private}} holds the consistent version of pages after each commit (and on reboot), while \texttt{\underline{shadow}} serves as support during the execution of coalesced tasks.
The VMM prohibits applications from directly accessing these buffers.
Instead, it redirects any request to the \texttt{working} buffer located in the volatile memory (SRAM), which has a lower latency and energy cost to access than FRAM.
It populates the \texttt{working} buffer with the privatized pages from non-volatile memory requested by tasks.
When a coalesced task completes, the VMM ensures that {\em dirty}, i.e., modified, pages are committed to FRAM and visible to subsequent tasks.
If a power failure interrupts a task, all temporary modifications to pages in \texttt{working} (and \texttt{\underline{shadow}}) occurred after the last commit are discarded in order to keep data consistency.
On a commit, the VMM atomically copies, through a two-phase commit, all dirty pages back into their location in the non-volatile memory.
% SRAM has a limited size and there is an extended working memory containing {\em shadow pages} in the larger FRAM. A shadow page stores the data from an updated page that needs to be committed back to non-volatile memory, but that exceeded the size of the volatile working memory.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/mem-man.pdf}
    \caption{Interaction between task, memory manager and memory buffers upon \texttt{RP} and \texttt{WP}, and order of occurrence. Steps 2, 3, 4 and 5 are conditional.}
    \label{figure:mem-man}
\end{figure}

@@

\begin{algorithm}[t]
    \captionof{algorithm}{\texttt{RP}(variable $v$)}
    \label{algo:rwar}
    \scriptsize
    \begin{algorithmic}[1]
		\State $t \leftarrow \Call{GetTag}{v}$
        \State $i \gets \{ j\ |\ \Call{GetTag}{\texttt{working}[j]} = t \}$ \Comment{Search page}
		\If { $i = \emptyset$ } \Comment{Variable in a resident page?}
		\State	$i \gets \Call{PageFault}{t}$ \Comment{Swap page in}
		\EndIf
		\State $o \leftarrow \Call{GetOffset}{v}$
		\State \Return \texttt{working}[$i$][$o$]  \Comment{Return from page}
	\end{algorithmic}
\end{algorithm}

@@

To make the commit atomic, \sys commits dirty pages in two phases, as shown in Algorithm~\ref{algo:commit}. The first phase copies dirty pages from \texttt{working} to the non-volatile \texttt{\underline{shadow}} (Line 4). The second phase commits pages from \texttt{\underline{shadow}} to \texttt{\underline{private}} (Line 12).  If power fails during the first phase, the whole commit is aborted, and the execution restarts from the most recently committed point (i.e., from the beginning of a coalesced task). If power fails in the second
phase, the commit process safely resumes on reboot.  The second phase depends on some run-time metadata. The \texttt{\underline{committing}} bit indicates that a commit is in progress and is set before the first page is committed (Line 9) and cleared after the last page is committed (Line 16).  The \texttt{\underline{shadowCount}} records the number of dirty shadow pages to commit and the VMM clears the counter when commit completes (Line 14). The \texttt{\underline{commitIndex}} indexes the next page to be committed (Line 11) and the VMM clears the index at the end of the phase (Line 15).

@@

\begin{algorithm}[t]
	\caption{Two-phase commit}
	\label{algo:commit}
	\scriptsize
	\begin{algorithmic}[1]
        \Procedure{CommitPhase1}{} \Comment{On last coalesced task}
            \For {$i \in 0..|\texttt{working}|-1$}
                \State $t \gets \Call{Tag}{\texttt{working}[i]}$
                \State $\texttt{\underline{shadow}}[\Call{Tag}{\texttt{working}[i]}] \xleftarrow{\text{DMA}} \texttt{working}[i]$
                \State $\texttt{\underline{shadowList}}[\texttt{\underline{shadowCount}}] \gets t$
                \State $\texttt{\underline{shadowCount}} \gets \texttt{\underline{shadowCount}} + 1$
            \EndFor
            \State \Call{CommitPhase2}{}
        \EndProcedure
        \Procedure{CommitPhase2}{} \Comment{\texttt{\underline{commitIndex}} 0 on first boot}
            \State $\texttt{\underline{committing}} \gets \textbf{true}$
            \While{\texttt{\underline{commitIndex}} < \texttt{\underline{shadowCount}}}
                \State $t \gets \texttt{\underline{shadowList}}[\texttt{\underline{commitIndex}}]$
                \State \Call{commitToPrivate}{\texttt{\underline{shadow}}[t]}
                \State $\texttt{\underline{commitIndex}} \gets \texttt{\underline{commitIndex}} + 1$
            \EndWhile
            \State $\texttt{\underline{shadowCount}} \gets 0$
            \State $\texttt{\underline{commitIndex}} \gets 0$
            \State $\texttt{\underline{committing}} \gets \textbf{false}$
        \EndProcedure
        \Procedure{OnBoot}{} \Comment{Invoked on every boot}
            \If { \texttt{\underline{committing}} } \Call{CommitPhase2}{}
            \EndIf
            \State $\texttt{\underline{shadowCount}} \gets 0$, $i_\text{victim} \gets 0$
        \EndProcedure
	\end{algorithmic}
\end{algorithm}

@@

\sys asks the programmer to use its {\tt RP} and {\tt WP} API methods on every access to a protected variable (cf. Section~\ref{sec:coala_api}). These API invocations present a risk of high overhead because there is a dynamic check on every read and write. Despite the risk of per-access overhead, \sys's dynamic memory protection scheme brings several benefits over a static approach (i.e.,~\cite{alpaca}). First, the limitations of static analysis preclude some uses of pointers due to potential pointer aliasing. For example, in the presence of arbitrary pointer operations, a function call using a function pointer, or an interrupt within a task, the system cannot statically analyze the memory behavior. Second, a static approach \textit{cannot handle task coalescing}, because a protected variable's lifetime, i.e., from first use to commit, is unknown at compile-time. \sys's dynamic, per-access instrumentation supports arbitrary use of pointers and enables task coalescing.

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.8\columnwidth]{figures/coalesced-war.pdf}
	\caption{Task coalescing-induced WAR dependency (in the case of this example, at variable $x$). Such dynamic dependencies cannot be resolved at compile-time and they break memory consistency.}
	\label{figure:coalescedWar}
\end{figure}

@@

VMM overview is given in Fig.~\ref{figure:mem-man}.
VMM abstracts the physical address space of the non-volatile memory (FRAM) and divides it into \texttt{\underline{private}} and \texttt{\underline{shadow}} (underlined locations are non-volatile) buffers, and each buffer is divided into pages.
\texttt{\underline{private}} holds the consistent version of pages after each commit (and on a reboot), while \texttt{\underline{shadow}} serves as support during the execution of coalesced tasks.
The VMM prohibits applications from directly accessing these buffers.
Instead, it redirects any request to the \texttt{working} buffer located in the volatile memory (SRAM), which has a lower latency and energy cost to access than FRAM.
It populates the \texttt{working} buffer with the privatized pages from non-volatile memory requested by tasks.
When a coalesced task completes, the VMM ensures that {\em dirty}, i.e., modified, pages are committed to FRAM and visible to subsequent tasks.
If a power failure interrupts a task, all temporary modifications to pages in \texttt{working} (and \texttt{\underline{shadow}}) occurred after the last commit are discarded in order to keep data consistency.
On a commit, the VMM atomically copies, through a two-phase commit, all dirty pages back into their location in the non-volatile memory.
% SRAM has a limited size and there is an extended working memory containing {\em shadow pages} in the larger FRAM. A shadow page stores the data from an updated page that needs to be committed back to non-volatile memory, but that exceeded the size of the volatile working memory.

\begin{figure}
    \centering
    \includegraphics[width=0.8\columnwidth]{figures/mem-man.pdf}
    \caption{Interaction between task, memory manager and memory buffers upon \texttt{RP} and \texttt{WP}, and order of occurrence. Steps 2, 3, 4 and 5 are conditional.}
    \label{figure:mem-man}
\end{figure}

@@

\begin{algorithm}[t]
    \captionof{algorithm}{\texttt{RP}(variable $v$)}
    \label{algo:rwar}
    \small
    \begin{algorithmic}[1]
		\State $t \leftarrow \Call{GetTag}{v}$
        \State $i \gets \{ j\ |\ \Call{GetTag}{\texttt{working}[j]} = t \}$ \Comment{Search page}
		\If { $i = \emptyset$ } \Comment{Variable in a resident page?}
		\State	$i \gets \Call{PageFault}{t}$ \Comment{Swap page in}
		\EndIf
		\State $o \leftarrow \Call{GetOffset}{v}$
		\State \Return \texttt{working}[$i$][$o$]  \Comment{Return from page}
	\end{algorithmic}
\end{algorithm}

@@

To make the commit atomic, \sys commits dirty pages in two phases, as shown in Algorithm~\ref{algo:commit}. The first phase copies dirty pages from \texttt{working} to the non-volatile \texttt{\underline{shadow}} (Line 4). The second phase commits pages from \texttt{\underline{shadow}} to \texttt{\underline{private}} (Line 12).  If power fails during the first phase, the whole commit is aborted, and the execution restarts from the most recently committed point (i.e., from the beginning of a coalesced task). If power fails in the second
phase, the commit process safely resumes on reboot.  The second phase depends on some run-time metadata. The \texttt{\underline{committing}} bit indicates that a commit is in progress and is set before the first page is committed (Line 9) and cleared after the last page is committed (Line 16).  The \texttt{\underline{shadowCount}} records the number of dirty shadow pages to be committed and the VMM clears the counter when commit completes (Line 14). The \texttt{\underline{commitIndex}} indexes the next page to be committed (Line 11) and the VMM clears the index at the end of the phase (Line 15).

@@

\begin{algorithm}[t]
	\caption{Two-phase commit}
	\label{algo:commit}
	\small
	\begin{algorithmic}[1]
        \Procedure{CommitPhase1}{} \Comment{On last coalesced task}
            \For {$i \in 0..|\texttt{working}|-1$}
                \State $t \gets \Call{Tag}{\texttt{working}[i]}$
                \State $\texttt{\underline{shadow}}[\Call{Tag}{\texttt{working}[i]}] \xleftarrow{\text{DMA}} \texttt{working}[i]$
                \State $\texttt{\underline{shadowList}}[\texttt{\underline{shadowCount}}] \gets t$
                \State $\texttt{\underline{shadowCount}} \gets \texttt{\underline{shadowCount}} + 1$
            \EndFor
            \State \Call{CommitPhase2}{}
        \EndProcedure
        \Procedure{CommitPhase2}{} \Comment{\texttt{\underline{commitIndex}} 0 on first boot}
            \State $\texttt{\underline{committing}} \gets \textbf{true}$
            \While{\texttt{\underline{commitIndex}} < \texttt{\underline{shadowCount}}}
                \State $t \gets \texttt{\underline{shadowList}}[\texttt{\underline{commitIndex}}]$
                \State \Call{commitToPrivate}{\texttt{\underline{shadow}}[t]}
                \State $\texttt{\underline{commitIndex}} \gets \texttt{\underline{commitIndex}} + 1$
            \EndWhile
            \State $\texttt{\underline{shadowCount}} \gets 0$
            \State $\texttt{\underline{commitIndex}} \gets 0$
            \State $\texttt{\underline{committing}} \gets \textbf{false}$
        \EndProcedure
        \Procedure{OnBoot}{} \Comment{Invoked on every boot}
            \If { \texttt{\underline{committing}} } \Call{CommitPhase2}{}
            \EndIf
            \State $\texttt{\underline{shadowCount}} \gets 0$, $i_\text{victim} \gets 0$
        \EndProcedure
	\end{algorithmic}
\end{algorithm}

@@

\sys asks the programmer to use its {\tt RP} and {\tt WP} API methods on every access to a protected variable (Section~\ref{sec:coala_api}). These API invocations present a risk of high overhead because there is a dynamic check on every read and write. Despite the risk of per-access overhead, \sys's dynamic memory protection scheme brings several benefits over a static approach (i.e.,~\cite{alpaca}). First, the limitations of static analysis preclude some uses of pointers due to potential pointer aliasing. For example, in the presence of arbitrary pointer operations, a function call using a function pointer, or an interrupt within a task, the system cannot statically analyze the memory behavior. Second, a static approach \textit{cannot handle task coalescing}, because a protected variable's lifetime, i.e., from first use to commit, is unknown at compile-time. \sys's dynamic, per-access instrumentation supports arbitrary use of pointers and enables task coalescing.

### 2019-06-24 paper/TOSN/systemdescription.tex
TOSN coala version
First iteration

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/system-overview.pdf}
	\caption{\sys top-level view. APP: application, ATS: adaptive task scheduler, VMM: Virtual Memory Manager, PM: physical memory.}
	\label{fig:system_overview}
\end{figure}

\sys is a new programming and execution model that supports adaptive task-based execution and eliminates restructuring and re-compilation of applications considering device's energy buffer. \sys addresses the challenges given in Section~\ref{sec:background} by making task-based intermittent applications portable in the sense of different energy storage sizes, while keeping their execution efficient. Fig.~\ref{fig:system_overview} shows an overview of \sys.

@@

\paragraph{Virtual Memory Manager.}
\sys virtual memory manager (VMM) is the key enabler to ensure memory consistency while coalescing tasks. VMM allows applications to interface with only fast volatile memory pages and privatizes the pages demanded by a coalesced task in order to solve a novel data consistency problem; namely \emph{task coalescing-induced WAR dependency}. VMM achieves page privatization by keeping all page modifications in non-volatile memory on a coalesced task transition. Section~\ref{sec:memory_virtulaization} outlines VMM.

>>>>

\begin{figure}
	\centering
	\includegraphics[width=.8\columnwidth]{figures/system-overview.pdf}
	\caption{\sys top-level view. APP: application, ATS: adaptive task scheduler, VMM: Virtual Memory Manager, PM: physical memory.}
	\label{fig:system_overview}
\end{figure}

\sys is a new programming and execution model that supports adaptive task-based execution and eliminates restructuring and re-compilation of applications considering the device's energy buffer. \sys addresses the challenges given in Section~\ref{sec:background} by making task-based intermittent applications portable in the sense of different energy storage sizes while keeping their execution efficient. Fig.~\ref{fig:system_overview} shows an overview of \sys.

@@

\paragraph{Virtual Memory Manager.}
\sys virtual memory manager (VMM) is the key enabler to ensure memory consistency while coalescing tasks. VMM allows applications to interface with only fast volatile memory pages and privatizes the pages demanded by a coalesced task in order to solve a novel data consistency problem; namely \emph{task coalescing-induced WAR dependency}. VMM achieves page privatization by keeping all page modifications in non-volatile memory on a coalesced task transition. Section~\ref{sec:memory_virtulaization} explains VMM.
